---
title: "R语言入门"
subtitle: "第一讲 R的获取和安装"
output: 
  revealjs::revealjs_presentation:
    incremental: false  # bullet是否渐进
    theme: sky  # 主题，对应的css在library/revealjs/revealjs-3.3.0.1/css/theme下
    center: true  # 垂直居中
    highlight: espresso  # 划重点的方式……
    transition: concave  # 幻灯片切换的方式
    self_contained: false
    reveal_plugins: ["search", "zoom", "notes", "chalkboard", "menu"]  
    # reveal.js的插件老牛逼了
    reveal_options: 
      slideNumber: true
      previewLinks: true
      chalkboard: 
        theme: chalkboard
        toggleNotesButton: true
      menu:
        numbers: true
# runtime: shiny
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. 

<small>For more details on using R Markdown see <http://rmarkdown.rstudio.com>.</small>

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

>- Bullet 1
>- Bullet 2
>- Bullet 3

## Use a zoom transition {data-transition="zoom"}

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

# Horizontal Slide 1

## Vertical Slide 1
Things will be on the screen.

<aside class="notes">
things will **NOT** be on the screen.
</aside>

## Vertical Slide 2

# Horizontal Slide 2
